### 2014-02-27 paper/retrofit.tex
tsni for rr

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{The embedding |specLang alpha (targetLang nop)|, where
$|targetLang nop| = (|tS|\times|tE|\times|te|\times|tv|, |->|)$}
\label{fig:embedding}
%}
\end{figure}

@@

\clearpage % TODO: remove again, but keep for now to not have the text be split across 4 pages.
\subsection{Formal Guarantees}

@@

@@

\begin{theorem}[TSNI]
\end{theorem}

\begin{lemma}
  \label{lemma:tsni}
  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
  \begin{equation} \label{eq:tsni-lemma-lhs}
  |ic1| \approx_{|il|} |ic2|
  \qquad \text{and} \qquad
  |ic1| |.->| |ic1'|
  \end{equation}
  then there exists a configuration |ic2'| such that
  \begin{equation} \label{eq:tsni-lemma-rhs}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2'|
  \ \text{.}
  \end{equation}
\end{lemma}

\begin{proof}
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
  the theorem holds for derivation sequences of length up to $n$, and show that it also
  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:tsni}, we get
  |ic''| with
  \begin{equation} \label{eq:tsni-proof-1}
  |ic1''| \approx_{|il|} |ic2''|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2''|
  \end{equation}
  Applying the induction hypothesis to
  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
  \begin{equation} \label{eq:tsni-proof-2}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2''| |.->|^* |ic2'|
  \end{equation}
  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
  us~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
  We proof the lemma by induction on the derivation
  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
  could have been used to make the reduction step.
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
    step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified. The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a new task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1|, they will get filtered
    by |erasef il| in |ic1'|.
    Lets consider the possible changes to |iS1|: If |it1| sends a
    message, then the corresponding queue in |iS1'| will contain one
    more message.  However, that message has the label of |it1| (or a higher
    label), and will thus get erased by |erasef il|.
    Finally, receiving or not receiving a message (by
    \textsc{I-recv} or \textsc{I-noRecv}) only changes the queue of
    task |it1|, which are erased from |iS1|.
    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.

    Therefore, after |ic2| has potentially executed some number of steps
    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first task |it1| and |it2| don't
    get erased and are thus equivalent.
    The task |it2| can now take exactly the same step as |it1|;  we only
    need to argue that the potential differences in |iS1| and |iS2| cannot
    have an influence on the execution (and we know |iS1| and |iS2| are
    |il| equivalent).
    Again, only send and receive will change |iS|, so we consider all
    rules that could have been used for~\eqref{eq:tsni-lemma-rhs}.  If
    a message is sent, then the message is added to the same queue.  This
    queue is either completely erased, or it is |il| equivalent.  In both
    cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
    When the tasks are receiving a message, then by the reduction rules
    we know that they first filter the queue by the label of |it1|.  We
    also know that the queues are equivalent when filtered by the less
    restrictive label |il|, thus the messages received (or dropped) from the
    queue are equivalent.
  \end{itemize}
\end{proof}

@@

>>>>

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{The embedding |specLang alpha (targetLang nop)|, where
|targetLang nop = (tS, tE, te, tv, ->)|}
\label{fig:embedding}
%}
\end{figure}

@@

\subsection{Formal Guarantees}

@@

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, our specification language |specLang alpha
(targetLang nop) = ((iS,its), .->, erasef il)|, where |its| is a task
list containing terms from the embeddeding.
%}

@@

\begin{theorem}[Concurrent specification language is TSNI]
For any target language |targetLang nop|,
|specLang roundrobinf (targetLang nop)| satisfies TSNI.
\end{theorem}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cut{
\begin{lemma}
  \label{lemma:tsni}
  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
  \begin{equation} \label{eq:tsni-lemma-lhs}
  |ic1| \approx_{|il|} |ic2|
  \qquad \text{and} \qquad
  |ic1| |.->| |ic1'|
  \end{equation}
  then there exists a configuration |ic2'| such that
  \begin{equation} \label{eq:tsni-lemma-rhs}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2'|
  \ \text{.}
  \end{equation}
\end{lemma}

\begin{proof}
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
  the theorem holds for derivation sequences of length up to $n$, and show that it also
  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:tsni}, we get
  |ic''| with
  \begin{equation} \label{eq:tsni-proof-1}
  |ic1''| \approx_{|il|} |ic2''|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2''|
  \end{equation}
  Applying the induction hypothesis to
  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
  \begin{equation} \label{eq:tsni-proof-2}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2''| |.->|^* |ic2'|
  \end{equation}
  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
  us~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
  We proof the lemma by induction on the derivation
  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
  could have been used to make the reduction step.
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
    step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified. The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a new task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1|, they will get filtered
    by |erasef il| in |ic1'|.
    Lets consider the possible changes to |iS1|: If |it1| sends a
    message, then the corresponding queue in |iS1'| will contain one
    more message.  However, that message has the label of |it1| (or a higher
    label), and will thus get erased by |erasef il|.
    Finally, receiving or not receiving a message (by
    \textsc{I-recv} or \textsc{I-noRecv}) only changes the queue of
    task |it1|, which are erased from |iS1|.
    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.

    Therefore, after |ic2| has potentially executed some number of steps
    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first task |it1| and |it2| don't
    get erased and are thus equivalent.
    The task |it2| can now take exactly the same step as |it1|;  we only
    need to argue that the potential differences in |iS1| and |iS2| cannot
    have an influence on the execution (and we know |iS1| and |iS2| are
    |il| equivalent).
    Again, only send and receive will change |iS|, so we consider all
    rules that could have been used for~\eqref{eq:tsni-lemma-rhs}.  If
    a message is sent, then the message is added to the same queue.  This
    queue is either completely erased, or it is |il| equivalent.  In both
    cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
    When the tasks are receiving a message, then by the reduction rules
    we know that they first filter the queue by the label of |it1|.  We
    also know that the queues are equivalent when filtered by the less
    restrictive label |il|, thus the messages received (or dropped) from the
    queue are equivalent.
  \end{itemize}
\end{proof}
}
